Harmony: A Systems Programming Language and Model Checker

### 2022-01-16 paper/paper.tex
More improvements to paper

Modularity allows larger systems to be model checked in a way
that would not be tractable otherwise.
With Harmony, one can check the implementation of a lock separately,
but use the specification of the lock in the implementation of the
queue.  Similarly, one can check the implementation of a queue,
but then use the specification of the queue in a larger application.
Doing so is essentially a form of \emph{Partial Order Reduction}~\cite{Val91},
replacing the <{enqueue}> and <{dequeue}> implementations
by atomic actions.

>>>>

Modularity allows larger systems to be model checked in a way
that would not be tractable otherwise.
With Harmony, one can check the implementation of a lock separately,
but use the specification of the lock in the implementation of the
queue.  Similarly, one can check the implementation of a queue,
but then use the specification of the queue in a larger application.
Doing so is essentially a form of
\emph{Partial Order Reduction}~\cite{Owicki75,Lipton75,Val91},
replacing the <{enqueue}> and <{dequeue}> implementations
by atomic actions.
